---
title: "15-starter-code"
format: docx
editor: visual
---

## For Loops

For loops are used to perform a task for each 'item' in a sequence.

```{r}
for (i in 1:10) {
  print(i)
}
```

For loops can also iterate over objects. For example, let's create an empty vector and fill it in with numbers.

```{r}
# create empty vector
empty_vector <- vector(mode = "double", length = 7)

# fill in the vector with numbers equal to 1 + the index
for (i in seq_along(empty_vector)) {
  empty_vector[i] <- 1 + i
}

empty_vector
```

Sometimes we will only want to perform an action if a condition is met. Conditional statements pair well with for loops to accomplish this.

```{r}
empty_vector <- vector(mode = "double", length = 7)

for (i in seq_along(empty_vector)) {
  if (i == 1) {
    empty_vector[i] <- 1
  } else {
    empty_vector[i] <- sum(empty_vector[1:(i - 1)])
  }
}

empty_vector
```

Note that we can can condition on many possible values.

```{r}
empty_vector <- vector(mode = "double", length = 7)

for (i in seq_along(empty_vector)) {
  if (i == 1) {
    empty_vector[i] <- 0
  } else if (i == length(empty_vector)) {
    empty_vector[i] <- 0
  } else {
    empty_vector[i] <- 1 + empty_vector[i - 1]
  }
}

empty_vector
```

While a for loop is a powerful way to code an iteration and conditional statements give us even more flexibility, we might still need to copy and paste code to perform a task multiple times. In that case, we often want to use a **function**.

```{r}
multiply_xy <- function(x, y = 2) {
  return(x * y)
}

multiply_xy(2)

multiply_xy(x = 2, y = 4)
```

## Live Coding

Write a function that takes a data object as input and evaluates its type. Include evaluations for whether the data object is a string, a logical value, or numeric. You can use `is.character()`, `is.logical()` and `is.numeric()` to evaluate whether the data object corresponds to any of those types. The function should return a string that indicates the data type, i.e., `"string"`, `"logical"`, or `"numeric"`.

```{r}

```
